---
title: "Low cost"
author: "Andrés Camero"
date: "March 12, 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
library(rjson)
library(ggplot2)
library(stats)
library(reshape2)
library(plotly)

knitr::opts_chunk$set(dev = 'png')
setwd("~/git/dlopt/publications/low-cost/mae/results")
```


```{r echo=FALSE, warning=FALSE}

readMRSLog <- function(exec.log) {
  raw <- readLines(exec.log)
  ljson <- lapply(raw, function(x) {
    raw.json <- fromJSON(x)
    data.frame("p"=raw.json$metrics$p, 
               "log.p"=raw.json$metrics$log_p,
               "mean"=raw.json$metrics$mean,
               "std"=raw.json$metrics$std,
               "architecture"=paste(raw.json$architecture, collapse="-"),
               "nc"=sum(raw.json$architecture[2:(length(raw.json$architecture)-1)]),
               "lb"=raw.json$look_back,
               "hl"=length(raw.json$architecture)-2,
               "hl1"=raw.json$architecture[2],
               "hl2"=if(length(raw.json$architecture)>3) raw.json$architecture[3] else NA,
               "hl3"=if(length(raw.json$architecture)>4) raw.json$architecture[4] else NA)
  })
  mrs <- do.call(rbind.data.frame, ljson)
  return(mrs)
}

loadMRS <- function(path) {
  mrs.files <- list.files(path, pattern="mrs*")
  lmrs <- lapply(mrs.files, function(x) {
    readMRSLog(paste(path, x, sep="/"))
  })
  mrs <- do.call(rbind.data.frame, lmrs)
  mrs$architecture <- as.character(mrs$architecture)
  return(mrs)
}

readBPLog <- function(exec.log) {
  raw <- readLines(exec.log)
  ljson <- lapply(raw, function(x) {
    raw.json <- fromJSON(x)
    data.frame("mae"=raw.json$testing_metrics$mae,
               "mape"=raw.json$testing_metrics$mape,
               "architecture"=paste(raw.json$architecture, collapse="-"),
               "lb"=raw.json$look_back,
               "hl"=length(raw.json$architecture)-2,
               "hl1"=raw.json$architecture[2],
               "hl2"=if(length(raw.json$architecture)>3) raw.json$architecture[3] else NA,
               "hl3"=if(length(raw.json$architecture)>4) raw.json$architecture[4] else NA)
  })
  bp <- do.call(rbind.data.frame, ljson)
  return(bp)
}

loadBP <- function(path) {
  bp.files <- list.files(path, pattern="bp*")
  lbp <- lapply(bp.files, function(x) {
    readBPLog(paste(path, x, sep="/"))
  })
  bp <- do.call(rbind.data.frame, lbp)
  bp$architecture <- as.character(bp$architecture)
  return(bp)
}

```


```{r echo=FALSE, warning=FALSE}

#Data loading
sin.mrs <- loadMRS("sin")
sin.bp <- loadBP("sin")
sin <- merge(sin.bp, sin.mrs, by=c("architecture", "lb", "hl", "hl1", "hl2", "hl3"))

energy.mrs <- loadMRS("energy")
energy.bp <- loadBP("energy")
energy <- merge(energy.bp, energy.mrs, by=c("architecture", "lb", "hl", "hl1", "hl2", "hl3"))

parking.mrs <- loadMRS("birmingham")
parking.bp <- loadBP("birmingham")
parking <- merge(parking.bp, parking.mrs, by=c("architecture", "lb", "hl", "hl1", "hl2", "hl3"))

```


```{r echo=FALSE, warning=FALSE}

#Correlation

cor(sin[sin$hl==1,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(sin[sin$hl==2,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(sin[sin$hl==3,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(sin[,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])

cor(energy[energy$hl==1,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(energy[energy$hl==2,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(energy[energy$hl==3,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(energy[,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])

cor(parking[parking$hl==1,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(parking[parking$hl==2,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(parking[parking$hl==3,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])
cor(parking[,c("mae", "mape", "nc", "lb", "mean", "std", "log.p", "p")])


df <- sin
df <- parking
df <- energy

cor(df[df$hl==1, c("mae", "nc", "lb", "mean", "std", "log.p")])
cor(df[df$hl==2, c("mae", "nc", "lb", "mean", "std", "log.p")])
cor(df[df$hl==3, c("mae", "nc", "lb", "mean", "std", "log.p")])
cor(df[, c("mae", "nc", "lb", "mean", "std", "log.p")])

```


```{r echo=FALSE, warning=FALSE}
df <- sin
df <- parking
df <- energy

df <- df[df$hl==1,]

model <- lm( mae~log.p, data=df)
pl <- ggplot(df, aes(x=log.p, y=mae))
pl <- pl + geom_point(aes(color=as.factor(lb), shape=as.factor(hl)))
pl <- pl + stat_function(fun=function(x) {model$coefficients[1] + model$coefficients[2]*x})
pl <- pl + guides(color=guide_legend("LB"), shape=guide_legend("HL"))
pl <- pl + labs(x="log P", y="MAE") 
pl <- pl + theme_minimal()
plot(pl)

pl <- ggplot(df[df$hl==1,], aes(x=log.p, y=mae))
pl <- pl + geom_point(aes(color=as.factor(lb), shape=as.factor(hl)))
pl <- pl + guides(color=guide_legend("LB"), shape=guide_legend("HL"))
pl <- pl + scale_y_log10()
pl <- pl + labs(x="log P", y="MAE") 
pl <- pl + theme_minimal()
plot(pl)


pl <- ggplot(df[df$hl==3,], aes(x=nc, y=log.p))
pl <- pl + geom_point(aes(color=as.factor(lb), shape=as.factor(hl)))
pl <- pl + guides(color=guide_legend("LB"), shape=guide_legend("HL"))
pl <- pl + labs(x="Total number of neurons", y="log P") 
pl <- pl + theme_minimal()
plot(pl)


```


```{r echo=FALSE, warning=FALSE}
df <- sin
df <- parking
df <- energy

df <- df[df$hl==2,]

surface <- acast(df[which(df$hl==2 & df$lb==2),], hl1~hl2, value.var="log.p")
p3d <- plot_ly(z=surface) %>%
  add_surface(contours = list(
    z = list(
      show=TRUE,
      usecolormap=TRUE,
      highlightcolor="#ff0000",
      project=list(z=TRUE)
      )
    ))
p3d
```


```{r echo=FALSE, warning=FALSE}

# Ajuste lineal MAE ~ log(P)

fit.obs <- function(data, seed, print=FALSE) {
  set.seed(seed)
  split <- as.integer(nrow(data)*.8)
  train <- sample(nrow(data), split)
  test <- seq(1, nrow(data), 1)[!(1:nrow(data) %in% train)]
  model <- lm( mae ~ log.p , data=data[train,])
  sm <- summary(model)
  test.data <- as.data.frame(predict.lm(model, data[test,]))
  colnames(test.data) <- c("predicted")
  test.data$observed <- data$mae[test]
  test.data$log.p <- data$log.p[test]
  test.data$predicted.decil <- as.integer(cut(test.data$predicted, quantile(test.data$predicted, probs = 0:10/10), include.lowest = TRUE))
  test.data$observed.decil <- as.integer(cut(test.data$observed, quantile(test.data$observed, probs = 0:10/10), include.lowest = TRUE))
  test.data$diff.decil <- test.data$observed.decil - test.data$predicted.decil
  cor.res <- cor.test(test.data$predicted.decil, test.data$observed.decil, method="spearman")
  one.diff <- sum(test.data$diff.decil %in% c(-1,0,1) ) / nrow(test.data)
  two.diff <- sum(test.data$diff.decil %in% c(-2,-1,0,1,2) ) / nrow(test.data)
  output <- data.frame("intercept"=sm$coefficients[1,1], "residual.std.error"=sm$sigma, "perc.error"=sm$sigma/sm$coefficients[1,1], "f.stat"=sm$fstatistic[1], "cor.estimate"=cor.res$estimate, "cor.p.value"=cor.res$p.value, "one.diff.perc"=one.diff, "two.diff.perc"=two.diff)
  if(print) {
    p1 <- ggplot(data=test.data, aes(x=observed, y=predicted)) + theme_minimal() 
    p1 <- p1 + geom_point(aes(color=abs(diff.decil)))
    p1 <- p1 + scale_color_continuous(low="green", high="red", na.value = "green", breaks=1:max(test.data$diff.decil))
    p1 <- p1 + labs(x="Observed MAE", y="Predicted MAE") 
    #p1 <- p1 + stat_function(fun=function(x) x) 
    p1 <- p1 + theme_minimal()
    p1 <- p1 + guides(color=guide_legend("Absolute\nDiff. Dec."))
    plot(p1)
    
    p2 <- ggplot(data=test.data, aes(x=log.p, y=observed)) + theme_minimal() 
    p2 <- p2 + geom_point(aes(color=abs(diff.decil)))
    p2 <- p2 + scale_color_continuous(low="green", high="red", na.value = "green", breaks=1:max(test.data$diff.decil))
    p2 <- p2 + labs(x="log P", y="Observed MAE")
    p2 <- p2 + stat_function(fun=function(x) {sm$coefficients[1,1] + sm$coefficients[2,1]*x})
    p2 <- p2 + guides(color=guide_legend("Absolute\nDiff. Dec."))
    p2 <- p2 + theme_minimal()
    plot(p2)
    
    p3 <- ggplot(data=test.data, aes(x=diff.decil, fill=as.factor(abs(diff.decil))))
    p3 <- p3 + geom_histogram(binwidth = 1)
    p3 <- p3 + labs(x="Difference between decile observed and predicted", y="Frequency")
    p3 <- p3 + theme_minimal()
    p3 <- p3 + scale_fill_manual(values=scales::seq_gradient_pal("green", "red", "Lab")(seq(0,1,length.out=10)), guide=FALSE)
    plot(p3)
  }
  return(output)
}

```


```{r echo=FALSE, warning=FALSE}
df <- sin
df <- energy
df <- parking

lms.df <- lapply(1:30, function(s){ fit.obs(df, seed=s) })
lms.df <- do.call(rbind.data.frame, lms.df)
colMeans(lms.df)

a <- fit.obs(df, seed=10, print=TRUE)

```



```{r echo=FALSE, warning=FALSE}

# Comparación de a pares
pairwise.comp <- function(df, tolerance=0.01) {
  archs <- nrow(df)
  cmp.eq <- 0
  n <- 0
  gg <- 0
  gl <- 0
  lg <- 0
  ll <- 0
  gg.tol <- 0
  gl.tol <- 0
  lg.tol <- 0
  ll.tol <- 0
  for(x in 1:archs) {
    for(y in 1:archs) {
      if(x != y) {
        n <- n + 1
        
        # Fuzzy with out tolerance
        if( df$log.p[x] >= df$log.p[y] && df$mae[x] <= df$mae[y]) {
          gl <- gl + 1
        } else if( df$log.p[x] >= df$log.p[y] && df$mae[x] >= df$mae[y]) {
          gg <- gg + 1
        } else if( df$log.p[x] <= df$log.p[y] && df$mae[x] >= df$mae[y]) {
          lg <- lg + 1
        } else {
          ll <- ll + 1
        }
        
        # Fuzzy with tolerance
        if( df$log.p[x] >= df$log.p[y] && (df$mae[x] <= df$mae[y] || abs(1- (df$mae[x]/df$mae[y])) <= tolerance) ) {
          gl.tol <- gl.tol + 1
        } else if( df$log.p[x] >= df$log.p[y] && (df$mae[x] >= df$mae[y] || abs(1- (df$mae[x]/df$mae[y])) <= tolerance)) {
          gg.tol <- gg.tol + 1
        } else if( df$log.p[x] <= df$log.p[y] && (df$mae[x] >= df$mae[y] || abs(1- (df$mae[x]/df$mae[y])) <= tolerance)) {
          lg.tol <- lg.tol + 1
        } else {
          ll.tol <- ll.tol + 1
        }
      }
    }
  }
  return(data.frame("N"=n, "GG"=gg, "GL"=gl, "LG"=lg, "LL"=ll, "GG.TOL"=gg.tol, "GL.TOL"=gl.tol, "LG.TOL"=lg.tol, "LL.TOL"=ll.tol))
}

cmp.sin <- pairwise.comp(sin, tolerance = 0.05)
# Tolerance 0.01
#         N       GG       GL       LG       LL   GG.TOL   GL.TOL   LG.TOL   LL.TOL
#  98000100 17847254 31152796 31152796 17847254 17805137 31194913 31195309 17804741
cmp.energy <- pairwise.comp(energy)
cmp.parking <- pairwise.comp(parking)

